\begin{thebibliography}{1}

\bibitem{UMLSuperstructure}
\begin{flushleft}
OMG Unified Modeling Language (OMG UML), Superstructure. Version 2.4.1, 2011, Режим доступа: http://www.omg.org/spec/UML/2.4.1/ (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{DesignPatterns}
\begin{flushleft}
Gamma E., Helm R., Johnson R., Vlissides J. Design Patterns: Elements of Reusable Object-Oriented Software Gamma. New Jersey: Pearson Education, 1994. 395 p.
\end{flushleft}

\bibitem{DesignPatternSimilarityScoring}
\begin{flushleft}
Tsantalis N., Chatzigeorgiou A., Stephanides G., Halkidis S.T. Design Pattern Detection Using Similarity Scoring. Transactions on Software Engineering. 2006, vol. 32, issue 11. P. 896 – 909.
\end{flushleft}

\bibitem{SimilarityGraphVertices}
\begin{flushleft}
Blondel V.D., Van Dooren P. A Measure Of Similarity Between Graph Vertices. With Applications To Synonym Extraction And Web Searching. SIAM Review. 2004, vol. 46, no. 4. P. 647 – 666.
\end{flushleft}

\bibitem{DesignPatternTemplateMatching}
\begin{flushleft}
Dong J., Sun Y., Zhao Y. Design Pattern Detection by Template Matching. Proceedings of the 2008 ACM symposium on Applied computing. 2008. P. 765 – 769.
\end{flushleft}

\bibitem{SubgraphIsomorphism}
\begin{flushleft}
Ullmann J.R., An Algorithm for Subgraph Isomorphism. Association for Computing Machinery. 1976, vol. 23, issue 1 P. 31 – 42.
\end{flushleft}

\bibitem{YAML}
\begin{flushleft}
The Official YAML Web Site, Режим доступа: http://yaml.org/ (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{plyj}
\begin{flushleft}
musiKk/plyj · GitHub --- A Java parser written in Python using PLY, Режим доступа: https://github.com/musiKk/plyj (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{javatools}
\begin{flushleft}
briencj/python-javatools · GitHub --- Tools for examining Java bytecode in Python, Режим доступа: https://github.com/obriencj/python-javatools (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{PyYAML}
\begin{flushleft}
PyYAML, Режим доступа: http://pyyaml.org/ (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{BCEL}
\begin{flushleft}
Apache Commons BCEL, Режим доступа: https://commons.apache.org/proper/commons-bcel/ (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{Maven}
\begin{flushleft}
Apache Maven Project, Режим доступа: https://maven.apache.org/ (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{pytest}
\begin{flushleft}
pytest, Режим доступа: http://pytest.org/ (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{PyHamcrest}
\begin{flushleft}
hamcrest/PyHamcrest · GitHub --- Hamcrest matchers for Python, Режим доступа: https://github.com/hamcrest/PyHamcrest (дата обращения 13.06.2015).
\end{flushleft}

\bibitem{java-design-patterns}
\begin{flushleft}
iluwatar/java-design-patterns · GitHub --- Design pattern samples implemented in Java, Режим доступа: https://github.com/iluwatar/java-design-patterns (дата обращения 13.06.2015).
\end{flushleft}

\end{thebibliography}
